Spatial considerations in the analysis of biological conservation data: space is special

### 2017-01-11 paper_v3_EI.Rmd
Add files via upload

```{r eval=T, echo=F, message=F, warning=F, cache = TRUE}
# you will only need to run the lines below after 
# you have installed the packages on your computer
library(GISTools)
library(rgdal)
library(GWmodel)
library(repmis)
library(knitr)

@@

```{r, fig.width=9, echo = F, eval=T,  cache = T, message=F, warning=F, fig.cap=fig$cap("", "a) The raw data points with a transparency term to show density of points, and b) Data summed over OS 10km grid cells.")}
par(mfrow = c(1,2))
par(mar = c(0,0,1,0))
plot(os10m, lwd = 0.5)
plot(data.sp[os10m,], pch = 1, cex = 0.2, col = "#2525254C", add = T)
title("a)")
sh <-auto.shading(d.a$tree[d.a$tree>0], n = 7, cols=brewer.pal(7,'Reds'))
sh$breaks <- c(1,5,10,20,30,50)
choropleth(d.a, v = d.a$tree, sh, pch = 19, cex = 0.4, add = F)
plot(os10m, lwd = 0.5, add = T)
choro.legend(px = "topright", sh = sh, title("Trees per 10km sq"), cex = 0.7)
title("b)")
```

@@

plot(os10m, lwd = 0.5)
sh <-auto.shading(d.a$rain[d.a$rain > 0 ], n = 7,
	cols=brewer.pal(7,'Blues'))
choropleth(d.a, v = d.a$rain, sh, pch = 19, cex = 0.3, add = T)
choro.legend(px = "topright", sh = sh, cex = 1)
title("a)", cex.main = 1.5)

plot(os10m, lwd = 0.5)
sh <-auto.shading(d.a$pet[!is.na(d.a$pet)], n = 7,
	cols=brewer.pal(7,'YlOrRd'))
choropleth(d.a, v = d.a$pet, sh, pch = 19, cex = 0.3, add = T)
choro.legend(px = "topright", sh = sh, cex = 1)
title("b)", cex.main = 1.5)

plot(os10m, lwd = 0.5)
sh <-auto.shading(d.a$wqi[!is.na(d.a$wqi)], n = 7,
	cols=brewer.pal(7,'GnBu'))
choropleth(d.a, v = d.a$wqi, sh, pch = 19, cex = 0.3, add = T)
choro.legend(px = "topright", sh = sh, cex = 1)
title("c)", cex.main = 1.5)
```

@@

sh = auto.shading(m.gr2$d.a.wqi, n = 7, 
	cols = brewer.pal(7, "Spectral"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, m.gr2$d.a.wqi, sh, pch = 19, cex = cx, add = T)
txt=expression(paste("GW WQI: ", B[PET]))
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = txt)
tit <- sprintf("WQI Global Coeff: %s",round(coef(m)[4], 3))
title(tit)
plot(os10m, lwd = 0.5, add = T)
```

@@

## 4.3 Final GWR analysis

@@

# Map Original GWR coefficient estimates and LCR GWR ones
# PET and GW coefs for PET 
par(mar = c(1,1,1,1))
par(mfrow = c(1,3)) 
cx <- 0.4
sh = auto.shading(m.gr2$d.a.pet, n = 7, 
	cols = brewer.pal(7, "Blues"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, m.gr2$d.a.pet, sh, pch = 19, cex = cx, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = "GWR Coeff")
tit <- sprintf("GWR PET Coeffs")
title(tit)

plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr3, m.gr3$d.a.pet, sh, pch = 19, cex = cx, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = "LCR-GWR Coeff")
tit <- sprintf("LCR GWR PET Coeffs")
title(tit)

val <- (m.gr2$d.a.pet - m.gr3$d.a.pet)
sh = auto.shading(val, n = 7, 
	cols = brewer.pal(7, "Spectral"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, val, sh, pch = 19, cex = cx, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = "Difference")
tit <- sprintf("LCR GWR vs GWR PET Coeffs")
title(tit)
```

@@

# WQI and GW coefs for WQI
par(mar = c(1,1,1,1))
par(mfrow = c(1,3)) 
cx <- 0.4
sh = auto.shading(m.gr2$d.a.wqi, n = 7, 
	cols = brewer.pal(7, "Greens"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, m.gr2$d.a.wqi, sh, pch = 19, cex = cx, add = T)
txt=expression(paste("GW Coeff: ",B[PET]))
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = txt)
tit <- sprintf("GWR WQI Coeffs")
title(tit)

plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr3, m.gr3$d.a.wqi, sh, pch = 19, cex = cx, add = T)
txt=expression(paste("LCR GW Coeff: ",B[PET]))
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = txt)
tit <- sprintf("LCR GWR WQI Coeffs")
title(tit)

val <- (m.gr2$d.a.wqi - m.gr3$d.a.wqi)
sh = auto.shading(val, n = 7, 
	cols = brewer.pal(7, "Spectral"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, val, sh, pch = 19, cex = cx, add = T)
txt= "Diff"
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7, title = txt)
tit <- sprintf("LCR GWR vs GWR WQI Coeffs")
title(tit)
```

>>>>

```{r eval=T, echo=F, message=F, warning=F, cache = F}
# you will only need to run the lines below after 
# you have installed the packages on your computer
library(GISTools)
library(rgdal)
library(GWmodel)
library(repmis)
library(knitr)

@@

```{r, fig.width=9, echo = F, eval=T,  cache = F, message=F, warning=F, fig.cap=fig$cap("", "a) The raw data points with a transparency term to show density of points, and b) Data summed over OS 10km grid cells.")}
par(mfrow = c(1,2))
par(mar = c(0,0,1,0))
plot(os10m, lwd = 0.5)
plot(data.sp[os10m,], pch = 1, cex = 0.2, col = "#2525254C", add = T)
title("a)")
sh <-auto.shading(d.a$tree[d.a$tree>0], n = 7, cols=brewer.pal(7,'Reds'))
sh$breaks <- c(1,5,10,20,30,50)
choropleth(d.a, v = d.a$tree, sh, pch = 19, cex = 0.4, add = F)
plot(os10m, lwd = 0.5, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, title="Trees per 10km sq", cex = 0.7)
title("b)")
```

@@

plot(os10m, lwd = 0.5)
sh <-auto.shading(d.a$rain[d.a$rain > 0 ], n = 7,
	cols=brewer.pal(7,'Blues'))
choropleth(d.a, v = d.a$rain, sh, pch = 19, cex = 0.3, add = T)
choro.legend(px = "topright", box.col = NA,sh = sh, cex = 1)
title("a)", cex.main = 1.5)

plot(os10m, lwd = 0.5)
sh <-auto.shading(d.a$pet[!is.na(d.a$pet)], n = 7,
	cols=brewer.pal(7,'YlOrRd'))
choropleth(d.a, v = d.a$pet, sh, pch = 19, cex = 0.3, add = T)
choro.legend(px = "topright", box.col = NA,sh = sh, cex = 1)
title("b)", cex.main = 1.5)

plot(os10m, lwd = 0.5)
sh <-auto.shading(d.a$wqi[!is.na(d.a$wqi)], n = 7,
	cols=brewer.pal(7,'GnBu'))
choropleth(d.a, v = d.a$wqi, sh, pch = 19, cex = 0.3, add = T)
choro.legend(px = "topright", box.col = NA,sh = sh, cex = 1)
title("c)", cex.main = 1.5)
```

@@

sh = auto.shading(m.gr2$d.a.wqi, n = 7, 
	cols = brewer.pal(7, "Spectral"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, m.gr2$d.a.wqi, sh, pch = 19, cex = cx, add = T)
txt=expression(paste("GW WQI: ", B[WQI]))
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.1f", cex = 0.7, title = txt)
tit <- sprintf("WQI Global Coeff: %s",round(coef(m)[4], 3))
title(tit)
plot(os10m, lwd = 0.5, add = T)
```

@@

## 4.3 Locally compensated ridge GWR analysis

@@

# Map Original GWR coefficient estimates and LCR GWR ones
# PET and GW coefs for PET 
par(mar = c(1,1,1,1))
par(mfrow = c(1,3)) 
cx <- 0.4
sh = auto.shading(m.gr2$d.a.pet, n = 7, 
	cols = brewer.pal(7, "Blues"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, m.gr2$d.a.pet, sh, pch = 19, cex = cx, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7)
tit <- sprintf("GWR PET Coeffs")
title(tit)

plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr3, m.gr3$d.a.pet, sh, pch = 19, cex = cx, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7)
tit <- sprintf("LCR GWR PET Coeffs")
title(tit)

val <- (m.gr2$d.a.pet - m.gr3$d.a.pet)
sh = auto.shading(val, n = 7, 
	cols = brewer.pal(7, "Spectral"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, val, sh, pch = 19, cex = cx, add = T)
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.2f", cex = 0.7)
tit <- sprintf("LCR GWR vs GWR PET Coeffs")
title(tit)
```

@@

# WQI and GW coefs for WQI
par(mar = c(1,1,1,1))
par(mfrow = c(1,3)) 
cx <- 0.4
sh = auto.shading(m.gr2$d.a.wqi, n = 7, 
	cols = brewer.pal(7, "Greens"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, m.gr2$d.a.wqi, sh, pch = 19, cex = cx, add = T)
txt=expression(paste("GW Coeff: ",B[PET]))
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.0f", cex = 0.7)
tit <- sprintf("GWR WQI Coeffs")
title(tit)

plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr3, m.gr3$d.a.wqi, sh, pch = 19, cex = cx, add = T)
txt=expression(paste("LCR GW Coeff: ",B[PET]))
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.0f", cex = 0.7)
tit <- sprintf("LCR GWR WQI Coeffs")
title(tit)

val <- (m.gr2$d.a.wqi - m.gr3$d.a.wqi)
sh = auto.shading(val, n = 7, 
	cols = brewer.pal(7, "Spectral"))
plot(os10m, lwd = 0.5, add = F)
choropleth(m.gr2, val, sh, pch = 19, cex = cx, add = T)
txt= "Diff"
choro.legend(px = "topright", sh = sh, box.col = NA, fmt = "%2.0f", cex = 0.7)
tit <- sprintf("LCR GWR vs GWR WQI Coeffs")
title(tit)
```
